Considering scale in multilayer animal social networks

### 2020-06-10 paper/manuscript.Rmd
new title
fst manuscript edits

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

# Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
among others. Meanwhile, in the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent.

@@

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across contexts, including scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female, (ii)
types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
used to describe multidimensional human social systems, complex transportation
networks, and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the social, spatial or temporal scales associated
with social systems.

@@

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers, and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and landcover context. Extending degree
centrality, we calculated multidegree, the sum of degree centrality of
individuals across layers, and neighbourhood, the sum of unique neighbours to
each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate layer relevance and connective redundancy. Layer
relevance is the proportion of neighbours present in each layer compared to the
neighbourhood for each individual and connective redundancy is the proportion of
neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across landcover classes
(e.g. summer open compared to winter open) using the Pearson correlation
coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
`igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].

@@

We modified the distance threshold, hereafter the social threshold, required for
group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
incremental distances between 5 - 500 m. For example, at the finest social
scale, only individuals within 5 m of one another were considered in the same
group, whereas at the coarsest social scale, individuals within 500 m of one
another were considered in the same group. We assumed these scales represented
visual (short distance) to auditory (long distance) sensory modalities of
caribou.

>>>>

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
among others. Meanwhile, in the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent.

@@

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female, (ii)
types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
used to describe multidimensional human social systems, complex transportation
networks, and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the social, spatial or temporal scales associated
with social systems.

@@

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers, and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and landcover context. Extending degree
centrality, we calculated multidegree, the sum of degree centrality of
individuals across layers, and neighbourhood, the sum of unique neighbours to
each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate layer relevance and connective redundancy. Layer
relevance is the proportion of neighbours present in each layer compared to the
neighbourhood for each individual and connective redundancy is the proportion of
neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across landcover classes
(e.g. summer open compared to winter open) using the Pearson correlation
coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
`igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].
<!-- add used spatsoc -->

@@

We modified the distance threshold, hereafter the social <!--distance-->threshold, required for
group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
incremental distances between 5 - 500 m. For example, at the finest social
scale, only individuals within 5 m of one another were considered in the same
group, whereas at the coarsest social scale, individuals within 500 m of one
another were considered in the same group. We assumed these scales represented
visual (short distance) to auditory (long distance) sensory modalities of
caribou.
